Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Transformed Validatability to use definition environments

\begin{defn}
  The degree to which a requirement is stated in terms that permit establishment
  of test criteria and performance (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn}
  Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\end{defn}

@@

Combo of definitions 4 and 5 ?

@@

\begin{itemize}
\item{Definition 1:} Validatability of a software is the degree of ease in
  validating(checking) that software meets user needs.
\item{Definition 2:} Validatability means ``solving the right
  equations''~\cite[p.~23]{Roache1998}.
\oo{question about this definition}
\item{Definition 3:} The degree of ease of evaluating software products or
  system to determine whether it satisfies specified business
  requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}
  \oo{Here I tweaked the meaning of validation to suit validatability}
  \oo{Only a few resource on validatability}
\end{itemize}

@@

Definition 3

>>>>

\begin{defn} \label{Defn_Verifiability1}
  The degree to which a requirement is stated in terms that permit establishment
  of test criteria and performance (\cite{IEEEStdGlossarySET1990}).
\end{defn}

\begin{defn} \label{Defn_Verifiability2}
  Ease of performing testing on a software product or system
  (\cite{IEEEStdGlossarySET1990}).
\end{defn}

@@

Combo of definitions~\ref{Defn_Verifiability1} and~\ref{Defn_Verifiability2} ?

@@

\begin{defn}
  Validatability of a software is the degree of ease in validating (checking)
  that software meets user needs.
\end{defn}

\begin{defn}
  Validatability means ``solving the right equations''~\cite[p.~23]{Roache1998}.
  \oo{question about this definition}
\end{defn}

\begin{defn} \label{DefnValidatability}
  The degree of ease of evaluating software products or system to determine
  whether it satisfies specified business
  requirements. \url{http://softwaretestingfundamentals.com/verification-vs-validation/}
  \oo{Here I tweaked the meaning of validation to suit validatability} \oo{Only
    a few resource on validatability}
\end{defn}

@@

Definition~\ref{DefnValidatability}.
